Weather Data Integration and Assimilation System\\

### 2020-02-13 results/sec_3-observations.tex
Fixed: “Section”
- Add “Section”
- “section” -> “Section”

According the \ref{se:test_plan} section, this section includes the observations after performing the test plans on the \acrshort{wdias} system setup and test plan test up which is explained in the \ref{se:workload}.

Sections \ref{subse:obs_test_plan_all_60min} to \ref{subse:obs_test_plan_all_auto_15min} discuss the observations collected with performing the Load test plans over 60 minutes (24 data points), 30 minutes (48 data points) and 15 minutes (96 data points) by variate the request size. Then another performance test with enabling Auto Scaling as explained in \ref{subse:test_plan_metrics} for high resource utilized microservice.

@@

\begin{table}[ht]
\caption{Throughput and Latency of load testing with 60min data}
\footnotesize
\begin{tabulary}{\linewidth}{|L|C|C|C|C|C|C|C|C|}
\hline
Label & \# Samples & Avg & Min & Max & 90\% Line & Std. Dev. & Error \% & RPS \\ \hline
Insert Timeseries & 71826 & 28 & 13 & 2773 & 31 & 58.74 & 0.00\% & 40.5 \\ \hline
Retrieve Timeseries & 71796 & 8 & 7 & 242 & 10 & 4.18 & 0.00\% & 40.7 \\ \hline
Insert Grid & 7982 & 23 & 21 & 126 & 26 & 4.23 & 0.06\% & 4.5 \\ \hline
Retrieve Grid & 7979 & 68 & 59 & 238 & 75 & 10.11 & 0.00\% & 4.5 \\ \hline
Query: Location & 71804 & 3 & 2 & 109 & 3 & 1.52 & 0.00\% & 40.5 \\ \hline
\textbf{TOTAL} & 311182 & 127 & 0 & 2773 & 503 & 207.80 & 0.00\% & 175.4 \\ \hline
\end{tabulary}
\label{tab:obs_all_60_min_summary}
\end{table}
Insert Timeseries performed over Scalar and Vector data types with each request send with 24 data points. On average it takes 28ms to insert data into the \acrshort{wdias}, and up to 90\% percentile inserted data within 31ms. Noticeably it has 0\% of errors which means that all the request are completed successfully. On average, \acrshort{wdias} handled 40.5 \acrshort{rps} with the given workload. The performance of the Retrieve of Scalar and Vector Timeseries are similar to insert timeseries due to it depends on it.
On the other hand, Insert Grid Timeseries data perform with 23ms with almost all the request perform within same amount of time, hence the standard deviation is smaller. Retrieve Grid Timeseries data perform the same but with bit higher value of latency of 68ms. Both of insert and retrieve grid timeseries data have 4.5 \acrshort{rps} since it only get 10\% of the number of request per given time via the test plan as explain in the data ration in \ref{se:test_plan}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Load Testing with 30min data (Request size = 48)}
\label{subse:obs_test_plan_all_30min}
This section \ref{subse:obs_test_plan_all_30min} discussed about the All test plan performance with 30 minutes data which means 48 data points per each request in Scalar and Vector timeseries, and 48 ASCII grid files per each insert request. It performed round up to 311k of sample requests which is almost similar to \ref{subse:obs_test_plan_all_60min} processed samples.

\begin{table}[ht]
\caption{Throughput and Latency of load test with 30min data}
\footnotesize
\begin{tabulary}{\linewidth}{|L|C|C|C|C|C|C|C|C|}
\hline
Label & \# Samples & Average & Min & Max & 90\% Line & Std. Dev. & Error \% & RPS \\ \hline
Insert Timeseries & 71759 & 29 & 14 & 1699 & 32 & 50.97 & 0.00\% & 40.5 \\ \hline
Retrieve Timeseries & 71730 & 9 & 7 & 1033 & 10 & 6.04 & 0.00\% & 40.6 \\ \hline
Insert Grid & 7972 & 44 & 40 & 162 & 49 & 8.17 & 0.08\% & 4.5 \\ \hline
Retrieve Grid & 7971 & 81 & 67 & 284 & 93 & 15.15 & 0.00\% & 4.5 \\ \hline
Query: Location & 71734 & 3 & 2 & 110 & 3 & 1.90 & 0.00\% & 40.5 \\ \hline
TOTAL & 310878 & 129 & 0 & 1699 & 503 & 207.10 & 0.00\% & 175.3 \\ \hline
\end{tabulary}
\label{tab:obs_all_30_min_summary}
\end{table}
\ref{tab:obs_all_30_min_summary} shows the response latency summary details and \acrshort{rps} as explained in \ref{subse:obs_test_plan_all_60min}. And the results are almost similar to the observations in \ref{tab:obs_all_60_min_summary}. This implies that, even the request size is increased, the \acrshort{wdias} can perform better same as the with smaller size of data.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Load Testing with 15min data (96 Request Size)}
\label{subse:obs_test_plan_all_15min}
This section \ref{subse:obs_test_plan_all_15min} discussed about the All test plan performance with 15 minutes data which means 96 data points per each request in Scalar and Vector timeseries, and 96 ASCII Grid files per each insert Grid timeseries request. These requests are four times larger than the \ref{subse:obs_test_plan_all_60min} request size. It performed approximately 311k of sample requests which is almost similar to \ref{subse:obs_test_plan_all_30min} processed samples.
\begin{table}[ht]
\caption{Throughput and Latency of load testing with 15min data}
\footnotesize
\begin{tabulary}{\linewidth}{|L|C|C|C|C|C|C|C|C|}
\hline
Label & \# Samples & Average & Min & Max & 90\% Line & Std. Dev. & Error \% & RPS \\ \hline
Insert Timeseries & 71775 & 30 & 12 & 1719 & 41 & 51.71 & 0.00\% & 40.5 \\ \hline
Retrieve Timeseries & 71736 & 23 & 8 & 1623 & 32 & 50.18 & 0.00\% & 40.6 \\ \hline
Insert Grid & 7975 & 91 & 77 & 279 & 112 & 19.58 & 1.42\% & 4.5 \\ \hline
Retrieve Grid & 7972 & 118 & 80 & 876 & 165 & 56.15 & 0.00\% & 4.5 \\ \hline
Query: Location & 71749 & 3 & 2 & 130 & 4 & 2.32 & 0.00\% & 40.5 \\ \hline
\textbf{TOTAL} & 310934 & 134 & 0 & 1719 & 503 & 206.40 & 0.04\% & 175.4 \\ \hline
\end{tabulary}
\label{tab:obs_all_15_min_summary}
\end{table}
\ref{tab:obs_all_15_min_summary} shows the response latency summary details and \acrshort{rps} as same as explained in \ref{subse:obs_test_plan_all_30min}. And the latency observations are increased by some amount when compared to the observations in \ref{tab:obs_all_30_min_summary}. Noticeably retrieving latency of all type of data types increased by considerable amount. Same following the trend, standard deviation of retrieve timeseries data increased my considerable amount for all the types. We can assume that more writing to the databases affected on reads as well. Event the request data size increased by 4x time, the \acrshort{wdias} were able to handle them without any significant performance issues. And the system able to provide the same throughput as \ref{tab:obs_all_30_min_summary}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Load Testing with Auto Pod Scaling}
\label{subse:obs_test_plan_all_auto_15min}
This section \ref{subse:obs_test_plan_all_auto_15min} discussed about the All test plan performance with 15 minutes data which means 96 data points per each request in Scalar and Vector timeseries, and 96 ASCII Grid files per each insert Grid timeseries request. These requests are four times larger than the \ref{subse:obs_test_plan_all_60min} request size. It performed approximately 311k of sample requests which is almost similar to \ref{subse:obs_test_plan_all_15min} processed samples.
Other than that, this test plan runs with enabling \acrshort{k8s} Auto Scaling for the high resource utilized microservice as explained in the \ref{subse:test_plan_metrics}. With the test load used for the performance test, import-ascii-grid-upload microservice is using lots of CPU, and adapter-grid microservice is using lots of Memory. During this test plan, \acrshort{wdias} start with the auto scaling enabled for import-ascii-grid-upload microservice. Since adapter-grid is a consistence service for storing netCDF files, it is not possible to auto scale, since \acrshort{eks} does not support multiple read write support volumes \cite{LinuxFoundationPersistentKubernetes}.

\begin{table}[ht]
\caption{Throughput and Latency of load testing with 15min data while enabled \acrshort{k8s} Auto Scaling}
\footnotesize
\begin{tabulary}{\linewidth}{|L|C|C|C|C|C|C|C|C|}
\hline
Label & Samples & Avg & Min & Max & 90\% Line & Std. Dev. & Error \% & RPS \\ \hline
Insert Timeseries & 71727 & 34 & 13 & 1777 & 27 & 118.78 & 0.00\% & 40.5 \\ \hline
Retrieve Timeseries & 71693 & 7 & 5 & 1608 & 9 & 18.72 & 0.00\% & 40.5 \\ \hline
Insert Grid & 7968 & 87 & 77 & 233 & 98 & 14.07 & 0.18\% & 4.5 \\ \hline
Retrieve Grid & 7965 & 89 & 63 & 1694 & 110 & 37.79 & 0.00\% & 4.5 \\ \hline
Query: Location & 71704 & 1 & 0 & 203 & 2 & 2.05 & 0.00\% & 40.5 \\ \hline
\textbf{TOTAL} & 310734 & 130 & 0 & 1777 & 501 & 212.35 & 0.00\% & 175.3 \\ \hline
\end{tabulary}
\label{tab:obs_all_auto_15_min_summary}
\end{table}
\ref{tab:obs_all_auto_15_min_summary} shows the response latency summary details and \acrshort{rps} as same as explained in \ref{subse:obs_test_plan_all_15min}.
During this test plan. the main focus on the auto scaling enabled microservice. As per the insert grid latency in the \ref{tab:obs_all_auto_15_min_summary}, the average insert latency is reduced from 91ms to 87ms. Also error percentage reduced from 1.42\% to 0.18\%. Standard deviation reduced from 19.58 to 14.07 which means the latency is much closer to the average latency. These improvements in insert Grid timeseries data seems to affect on out put of retrieve Grid timeseries data as well.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Query Module Load Test}
\label{subse:obs_test_plan_query_15min}
This section \ref{subse:obs_test_plan_query_15min} discussed about the Query test plan performance. It performs multiple information retrieval queries such as query over locations, parameters and timeseries etc which are described over \ref{se:query}. It performed approximately 123k of sample requests.
Query test plan perform over 5 minutes of time period, and with a higher number of requests than other test plan with a peak of 600 hits per seconds.

>>>>

According the Section \ref{se:test_plan} section, this section includes the observations after performing the test plans on the \acrshort{wdias} system setup and test plan test up which is explained in the Section \ref{se:workload}.

Sections \ref{subse:obs_test_plan_all_60min} to \ref{subse:obs_test_plan_all_auto_15min} discuss the observations collected with performing the Load test plans over 60 minutes (24 data points), 30 minutes (48 data points) and 15 minutes (96 data points) by variate the request size. Then another performance test with enabling Auto Scaling as explained in Section \ref{subse:test_plan_metrics} for high resource utilized microservice.

@@

\begin{table}[ht]
\caption{Throughput and Latency of load testing with 60min data}
\footnotesize
\begin{tabulary}{\linewidth}{|L|C|C|C|C|C|C|C|C|}
\hline
Label & \# Samples & Avg & Min & Max & 90\% Line & Std. Dev. & Error \% & RPS \\ \hline
Insert Timeseries & 71826 & 28 & 13 & 2773 & 31 & 58.74 & 0.00\% & 40.5 \\ \hline
Retrieve Timeseries & 71796 & 8 & 7 & 242 & 10 & 4.18 & 0.00\% & 40.7 \\ \hline
Insert Grid & 7982 & 23 & 21 & 126 & 26 & 4.23 & 0.06\% & 4.5 \\ \hline
Retrieve Grid & 7979 & 68 & 59 & 238 & 75 & 10.11 & 0.00\% & 4.5 \\ \hline
Query: Location & 71804 & 3 & 2 & 109 & 3 & 1.52 & 0.00\% & 40.5 \\ \hline
\textbf{TOTAL} & 311182 & 127 & 0 & 2773 & 503 & 207.80 & 0.00\% & 175.4 \\ \hline
\end{tabulary}
\label{tab:obs_all_60_min_summary}
\end{table}
Insert Timeseries performed over Scalar and Vector data types with each request send with 24 data points. On average it takes 28ms to insert data into the \acrshort{wdias}, and up to 90\% percentile inserted data within 31ms. Noticeably it has 0\% of errors which means that all the request are completed successfully. On average, \acrshort{wdias} handled 40.5 \acrshort{rps} with the given workload. The performance of the Retrieve of Scalar and Vector Timeseries are similar to insert timeseries due to it depends on it.
On the other hand, Insert Grid Timeseries data perform with 23ms with almost all the request perform within same amount of time, hence the standard deviation is smaller. Retrieve Grid Timeseries data perform the same but with bit higher value of latency of 68ms. Both of insert and retrieve grid timeseries data have 4.5 \acrshort{rps} since it only get 10\% of the number of request per given time via the test plan as explain in the data ration in Section \ref{se:test_plan}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Load Testing with 30min data (Request size = 48)}
\label{subse:obs_test_plan_all_30min}
This Section \ref{subse:obs_test_plan_all_30min} discussed about the All test plan performance with 30 minutes data which means 48 data points per each request in Scalar and Vector timeseries, and 48 ASCII grid files per each insert request. It performed round up to 311k of sample requests which is almost similar to Section \ref{subse:obs_test_plan_all_60min} processed samples.

\begin{table}[ht]
\caption{Throughput and Latency of load test with 30min data}
\footnotesize
\begin{tabulary}{\linewidth}{|L|C|C|C|C|C|C|C|C|}
\hline
Label & \# Samples & Average & Min & Max & 90\% Line & Std. Dev. & Error \% & RPS \\ \hline
Insert Timeseries & 71759 & 29 & 14 & 1699 & 32 & 50.97 & 0.00\% & 40.5 \\ \hline
Retrieve Timeseries & 71730 & 9 & 7 & 1033 & 10 & 6.04 & 0.00\% & 40.6 \\ \hline
Insert Grid & 7972 & 44 & 40 & 162 & 49 & 8.17 & 0.08\% & 4.5 \\ \hline
Retrieve Grid & 7971 & 81 & 67 & 284 & 93 & 15.15 & 0.00\% & 4.5 \\ \hline
Query: Location & 71734 & 3 & 2 & 110 & 3 & 1.90 & 0.00\% & 40.5 \\ \hline
TOTAL & 310878 & 129 & 0 & 1699 & 503 & 207.10 & 0.00\% & 175.3 \\ \hline
\end{tabulary}
\label{tab:obs_all_30_min_summary}
\end{table}
\ref{tab:obs_all_30_min_summary} shows the response latency summary details and \acrshort{rps} as explained in Section \ref{subse:obs_test_plan_all_60min}. And the results are almost similar to the observations in \ref{tab:obs_all_60_min_summary}. This implies that, even the request size is increased, the \acrshort{wdias} can perform better same as the with smaller size of data.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Load Testing with 15min data (96 Request Size)}
\label{subse:obs_test_plan_all_15min}
This Section \ref{subse:obs_test_plan_all_15min} discussed about the All test plan performance with 15 minutes data which means 96 data points per each request in Scalar and Vector timeseries, and 96 ASCII Grid files per each insert Grid timeseries request. These requests are four times larger than the Section \ref{subse:obs_test_plan_all_60min} request size. It performed approximately 311k of sample requests which is almost similar to Section \ref{subse:obs_test_plan_all_30min} processed samples.
\begin{table}[ht]
\caption{Throughput and Latency of load testing with 15min data}
\footnotesize
\begin{tabulary}{\linewidth}{|L|C|C|C|C|C|C|C|C|}
\hline
Label & \# Samples & Average & Min & Max & 90\% Line & Std. Dev. & Error \% & RPS \\ \hline
Insert Timeseries & 71775 & 30 & 12 & 1719 & 41 & 51.71 & 0.00\% & 40.5 \\ \hline
Retrieve Timeseries & 71736 & 23 & 8 & 1623 & 32 & 50.18 & 0.00\% & 40.6 \\ \hline
Insert Grid & 7975 & 91 & 77 & 279 & 112 & 19.58 & 1.42\% & 4.5 \\ \hline
Retrieve Grid & 7972 & 118 & 80 & 876 & 165 & 56.15 & 0.00\% & 4.5 \\ \hline
Query: Location & 71749 & 3 & 2 & 130 & 4 & 2.32 & 0.00\% & 40.5 \\ \hline
\textbf{TOTAL} & 310934 & 134 & 0 & 1719 & 503 & 206.40 & 0.04\% & 175.4 \\ \hline
\end{tabulary}
\label{tab:obs_all_15_min_summary}
\end{table}
\ref{tab:obs_all_15_min_summary} shows the response latency summary details and \acrshort{rps} as same as explained in Section \ref{subse:obs_test_plan_all_30min}. And the latency observations are increased by some amount when compared to the observations in \ref{tab:obs_all_30_min_summary}. Noticeably retrieving latency of all type of data types increased by considerable amount. Same following the trend, standard deviation of retrieve timeseries data increased my considerable amount for all the types. We can assume that more writing to the databases affected on reads as well. Event the request data size increased by 4x time, the \acrshort{wdias} were able to handle them without any significant performance issues. And the system able to provide the same throughput as \ref{tab:obs_all_30_min_summary}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Load Testing with Auto Pod Scaling}
\label{subse:obs_test_plan_all_auto_15min}
This Section \ref{subse:obs_test_plan_all_auto_15min} discussed about the All test plan performance with 15 minutes data which means 96 data points per each request in Scalar and Vector timeseries, and 96 ASCII Grid files per each insert Grid timeseries request. These requests are four times larger than the Section \ref{subse:obs_test_plan_all_60min} request size. It performed approximately 311k of sample requests which is almost similar to Section \ref{subse:obs_test_plan_all_15min} processed samples.
Other than that, this test plan runs with enabling \acrshort{k8s} Auto Scaling for the high resource utilized microservice as explained in the Section \ref{subse:test_plan_metrics}. With the test load used for the performance test, import-ascii-grid-upload microservice is using lots of CPU, and adapter-grid microservice is using lots of Memory. During this test plan, \acrshort{wdias} start with the auto scaling enabled for import-ascii-grid-upload microservice. Since adapter-grid is a consistence service for storing netCDF files, it is not possible to auto scale, since \acrshort{eks} does not support multiple read write support volumes \cite{LinuxFoundationPersistentKubernetes}.

\begin{table}[ht]
\caption{Throughput and Latency of load testing with 15min data while enabled \acrshort{k8s} Auto Scaling}
\footnotesize
\begin{tabulary}{\linewidth}{|L|C|C|C|C|C|C|C|C|}
\hline
Label & Samples & Avg & Min & Max & 90\% Line & Std. Dev. & Error \% & RPS \\ \hline
Insert Timeseries & 71727 & 34 & 13 & 1777 & 27 & 118.78 & 0.00\% & 40.5 \\ \hline
Retrieve Timeseries & 71693 & 7 & 5 & 1608 & 9 & 18.72 & 0.00\% & 40.5 \\ \hline
Insert Grid & 7968 & 87 & 77 & 233 & 98 & 14.07 & 0.18\% & 4.5 \\ \hline
Retrieve Grid & 7965 & 89 & 63 & 1694 & 110 & 37.79 & 0.00\% & 4.5 \\ \hline
Query: Location & 71704 & 1 & 0 & 203 & 2 & 2.05 & 0.00\% & 40.5 \\ \hline
\textbf{TOTAL} & 310734 & 130 & 0 & 1777 & 501 & 212.35 & 0.00\% & 175.3 \\ \hline
\end{tabulary}
\label{tab:obs_all_auto_15_min_summary}
\end{table}
\ref{tab:obs_all_auto_15_min_summary} shows the response latency summary details and \acrshort{rps} as same as explained in Section \ref{subse:obs_test_plan_all_15min}.
During this test plan. the main focus on the auto scaling enabled microservice. As per the insert grid latency in the \ref{tab:obs_all_auto_15_min_summary}, the average insert latency is reduced from 91ms to 87ms. Also error percentage reduced from 1.42\% to 0.18\%. Standard deviation reduced from 19.58 to 14.07 which means the latency is much closer to the average latency. These improvements in insert Grid timeseries data seems to affect on out put of retrieve Grid timeseries data as well.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Query Module Load Test}
\label{subse:obs_test_plan_query_15min}
This Section \ref{subse:obs_test_plan_query_15min} discussed about the Query test plan performance. It performs multiple information retrieval queries such as query over locations, parameters and timeseries etc which are described over Section \ref{se:query}. It performed approximately 123k of sample requests.
Query test plan perform over 5 minutes of time period, and with a higher number of requests than other test plan with a peak of 600 hits per seconds.

### 2020-02-13 results/sec_4-discussion.tex
Fixed: “Section”
- Add “Section”
- “section” -> “Section”

In this section concludes the observations in \ref{se:observations} section against the performance metrics defines in \ref{subse:test_plan_metrics}.

The \emph{Latency} for each operation type kept constant over the whole test plan run time without any significant change. When the request size increased from 24 data points to 96 data points, the latency increase throw out the whole test plan with a smaller number. But for each test run the latency kept constant over the time.
During the \ref{subse:obs_test_plan_all_auto_15min} test run, the performance of the Grid data got better when compared to the \ref{subse:obs_test_plan_all_15min}. Which means by adding more resources to the \acrshort{wdias}, it can handle more workload on the system.

@@

When look into the \emph{resource utilization} of \acrshort{wdias}; since it is using the \acrshort{k8s} as the container orchestration system, it allows to scale up and cool down the system as required based on the workload. This demonstrate on the test plan of \ref{subse:obs_test_plan_all_auto_15min}, and the system get scale up to the maximum at the peak time. Then cool down to single pod after finishing the test cases.
Given above \acrshort{wdias} can run from 1 CPU node to nodes with 100 CPUs. As described in the \ref{se:microservice}, it uses the many of the concept of modern microservice architecture to create stateless, failover, redundant microservice to achieve such capabilities.

>>>>

In this section concludes the observations in Section \ref{se:observations} section against the performance metrics defines in Section \ref{subse:test_plan_metrics}.

The \emph{Latency} for each operation type kept constant over the whole test plan run time without any significant change. When the request size increased from 24 data points to 96 data points, the latency increase throw out the whole test plan with a smaller number. But for each test run the latency kept constant over the time.
During the Section \ref{subse:obs_test_plan_all_auto_15min} test run, the performance of the Grid data got better when compared to the Section \ref{subse:obs_test_plan_all_15min}. Which means by adding more resources to the \acrshort{wdias}, it can handle more workload on the system.

@@

When look into the \emph{resource utilization} of \acrshort{wdias}; since it is using the \acrshort{k8s} as the container orchestration system, it allows to scale up and cool down the system as required based on the workload. This demonstrate on the test plan of Section \ref{subse:obs_test_plan_all_auto_15min}, and the system get scale up to the maximum at the peak time. Then cool down to single pod after finishing the test cases.
Given above \acrshort{wdias} can run from 1 CPU node to nodes with 100 CPUs. As described in the Section \ref{se:microservice}, it uses the many of the concept of modern microservice architecture to create stateless, failover, redundant microservice to achieve such capabilities.

### 2020-02-13 summary/sec_1-conclusions.tex
Fixed: “Section”
- Add “Section”
- “section” -> “Section”

Based on the microservice architecture patterns and the nature of the weather metadata, the \acrshort{wdias} came up with the idea of hierarchical database structure in order to provide higher performance while store the weather data optimum. The system uses timeseries database for storing Scalar and Vector timeseries data, and using \acrshort{netCDF} for storing Grid timeseries data. And each database adapter uses concept of database per service which allows each microservice service to scale without interference from other microservices.
And it uses microservice sagas pattern for asynchronous data handling for requests with higher size. According to the section \ref{se:microservice}, it uses the many of the concept of modern microservice architecture to create stateless, failover, redundant microservice to achieve such capabilities.

@@

Load testing of \acrshort{wdias} was perform using the \acrshort{jmeter} tool's distributed testing capabilities. Then the test plans are performed with increasing the request size, and monitored the performance metrics. The system is setup on the \acrfull{eks} as per the configurations of \ref{subse:test_sys_config}. Based on the observations, the system were able to handle 300 \acrshort{rps} (which means 18,000 requests per minute) successfully with minimizing the error rate to zero. Also, while increasing the request size from 24 to 96 data points per scalar and vector timeseries, and number of ASCII Grid files from 24 to 96, the \acrshort{wdias} was able to perform same while keeping the latency constant without any significant change. During the performance test plans, the system were able to provide increase the throughput by keeping the latency constant while increasing the workload. Which exhibit the scalability of the system.
With the \acrshort{k8s} auto scaling, the \acrshort{wdias} were able to elastically adjust the number of pods according to the workload with auto scaling configurations. 
The results of \acrshort{wdias} shows that the system can run from 1 CPU node to nodes with few hundred CPUs.

>>>>

Based on the microservice architecture patterns and the nature of the weather metadata, the \acrshort{wdias} came up with the idea of hierarchical database structure in order to provide higher performance while store the weather data optimum. The system uses timeseries database for storing Scalar and Vector timeseries data, and using \acrshort{netCDF} for storing Grid timeseries data. And each database adapter uses concept of database per service which allows each microservice service to scale without interference from other microservices.
And it uses microservice sagas pattern for asynchronous data handling for requests with higher size. According to the Section \ref{se:microservice}, it uses the many of the concept of modern microservice architecture to create stateless, failover, redundant microservice to achieve such capabilities.

@@

Load testing of \acrshort{wdias} was perform using the \acrshort{jmeter} tool's distributed testing capabilities. Then the test plans are performed with increasing the request size, and monitored the performance metrics. The system is setup on the \acrfull{eks} as per the configurations of Section \ref{subse:test_sys_config}. Based on the observations, the system were able to handle 300 \acrshort{rps} (which means 18,000 requests per minute) successfully with minimizing the error rate to zero. Also, while increasing the request size from 24 to 96 data points per scalar and vector timeseries, and number of ASCII Grid files from 24 to 96, the \acrshort{wdias} was able to perform same while keeping the latency constant without any significant change. During the performance test plans, the system were able to provide increase the throughput by keeping the latency constant while increasing the workload. Which exhibit the scalability of the system.
With the \acrshort{k8s} auto scaling, the \acrshort{wdias} were able to elastically adjust the number of pods according to the workload with auto scaling configurations. 
The results of \acrshort{wdias} shows that the system can run from 1 CPU node to nodes with few hundred CPUs.

### 2020-02-13 summary/sec_2-research_limitations.tex
Fixed: “Section”
- Add “Section”
- “section” -> “Section”

\emph{Grid data performance}:
As mentioned in the \ref{se:discussion}, the adapter-grid is using a Python wrapper for netCDF FORTRAN implementation with parallel IO enabled. This has some performance issues as well as memory leak issues. Since each microservice in the \acrshort{wdias} independent of technology that can use to implement the service, it will increase the performance if the adapter-grid directly ported to netCDF with a low level language such as C or FORTRAN. They are some future work that can focus on improving the performance of grid data.

@@

\emph{Improve test cases}:
As described in detail with \ref{subse:closed_vs_open_workload}, for \acrshort{wdias} performance test uses Time Stepping Feedback loop with Concurrent Threads which is the best approach support by \acrshort{jmeter} at the moment. But using that it is not possible to get desired \acrshort{rps} for each test case within the test plan.
Because of this issue, the \acrshort{wdias} test plans further improved by removing redundant test cases such as create timeseries at the beginning. Having create timeseries at the beginning causes some issues such as most of the thread are working on that test case rather on required test cases. Still there may be some improvement that can be done.

\emph{Further improve hierarchical database performance}:
As further described in \ref{se:discussion}, it is possible to increase the performance of these bottlenecks much higher such as using \acrshort{influxdb} Commercial cluster support for high availability or horizontal scaling of \acrshort{influxdb}. With \acrshort{influxdb} cluster, it is possible to run multiple pods of adapter-scalar and adapter-vector for support more server hits per second.
Other than that, the \acrshort{wdias} performance can improve via partitioning the timeseries key space into multiple \acrshort{influxdb} instances. The adapter-scalar or adapter-vector can improve to plug multiple instance of \acrshort{influxdb} instances by changing the configurations. As an example, based on the key attribute \ref{subse:timeseries_key_attributes} Timeseries Type, the adapter-scalar can connect to four instance of \acrshort{influxdb} instances such as  External Historical, External Forecast, Simulated Historical, and Simulated Forecast etc.

@@

>>>>

\emph{Grid data performance}:
As mentioned in the Section \ref{se:discussion}, the adapter-grid is using a Python wrapper for netCDF FORTRAN implementation with parallel IO enabled. This has some performance issues as well as memory leak issues. Since each microservice in the \acrshort{wdias} independent of technology that can use to implement the service, it will increase the performance if the adapter-grid directly ported to netCDF with a low level language such as C or FORTRAN. They are some future work that can focus on improving the performance of grid data.

@@

\emph{Improve test cases}:
As described in detail with Section \ref{subse:closed_vs_open_workload}, for \acrshort{wdias} performance test uses Time Stepping Feedback loop with Concurrent Threads which is the best approach support by \acrshort{jmeter} at the moment. But using that it is not possible to get desired \acrshort{rps} for each test case within the test plan.
Because of this issue, the \acrshort{wdias} test plans further improved by removing redundant test cases such as create timeseries at the beginning. Having create timeseries at the beginning causes some issues such as most of the thread are working on that test case rather on required test cases. Still there may be some improvement that can be done.

\emph{Further improve hierarchical database performance}:
As further described in Section \ref{se:discussion}, it is possible to increase the performance of these bottlenecks much higher such as using \acrshort{influxdb} Commercial cluster support for high availability or horizontal scaling of \acrshort{influxdb}. With \acrshort{influxdb} cluster, it is possible to run multiple pods of adapter-scalar and adapter-vector for support more server hits per second.
Other than that, the \acrshort{wdias} performance can improve via partitioning the timeseries key space into multiple \acrshort{influxdb} instances. The adapter-scalar or adapter-vector can improve to plug multiple instance of \acrshort{influxdb} instances by changing the configurations. As an example, based on the key attribute Section \ref{subse:timeseries_key_attributes} Timeseries Type, the adapter-scalar can connect to four instance of \acrshort{influxdb} instances such as  External Historical, External Forecast, Simulated Historical, and Simulated Forecast etc.

@@

\dbc{Need a new section for Conclusions.}
